---
title: "Activity Monitoring"
author: "SF"
date: "15. Oktober 2015"
output: html_document
---

## Info about the data

It is now possible to collect a large amount of data about personal movement 
using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone 
Up. These type of devices are part of the “quantified self” movement – a group 
of enthusiasts who take measurements about themselves regularly to improve their 
health, to find patterns in their behavior, or because they are tech geeks.
A personal activity monitoring device collects data at 5 minute intervals 
through out the day. The data consists of two months of data from an anonymous 
individual collected during the months of October and November, 2012 and include 
the number of steps taken in 5 minute intervals each day.

## Loading and Preprocessing the data

The data was downloaded from the course website for Reproducible Research. 

```{r}
activity <- read.csv("activity.csv")
```

## Mean total number of steps per day

The total number of steps per day are calculated and a histogram of the total 
number of steps taken each day is plotted.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
```

```{r histogram}
days <- group_by(activity, date)
s_days <- summarize(days, steps=sum(steps, na.rm = TRUE))
hist(s_days$steps, breaks = 10, main = "Total number of steps per day", 
     xlab = "number of steps")
```

The mean and median of the total number of steps is calculated.

```{r m_steps}
summarize(s_days, mean = mean(steps, na.rm = TRUE), 
          median = median(steps, na.rm = TRUE))
```

## Average daily activity pattern

The mean of the average number of steps per time intervall per day is taken and 
plotted.

```{r dailyactivity}
steps <- group_by(activity, interval)
a_steps <- summarize(steps, steps = mean(steps, na.rm = TRUE))
plot(a_steps$interval, a_steps$steps, type = "l")
